Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Add more comments

%% State the problem.
%% Say why it's an interesting problem.
%% Say what your solution achieves.
%% Say what follows from your solution.

@@

\begin{quote}
    TBD: state that ``A library for reusable pieces of specification would be
    useful.''
\begin{itemize}
    \item
        In Section~\ref{sec:reusable-specs}, we showed how to reuse
        pieces of specification.
    \item
        It would be possible and useful to write a library that
        provides reusable pieces of specification, for many of
        Haskell's standard classes.
        (similar in purpose to
        {\tt
        checkers}\footnote{http://hackage.haskell.org/package/checkers})
      \item copied here from Section~\ref{sec:reuseable-pecs}:

@@

\begin{quote}
    TBD: Add "best current practice"
\end{quote}

>>>>

\begin{itemize}
    \item We show how to reuse pieces of specifications (and/or that
        specifications are composable?).
\end{itemize}

\begin{itemize}
    \item State the problem.
    \item Say why it's an interesting problem.
    \item Say what your solution achieves.
    \item Say what follows from your solution.
\end{itemize}

@@

\begin{quote}
    TBD: state that ``A library for reusable pieces of specification would be
    useful.''
\begin{itemize}
    \item
        In Section~\ref{sec:reusable-specs}, we showed how to reuse
        pieces of specification.
    \item
        We think a library of reuseable specs would be a good idea
    \item
        It would be possible and useful to write a library that
        provides reusable pieces of specification, for many of
        Haskell's standard classes.
        (similar in purpose to
        {\tt
        checkers}\footnote{http://hackage.haskell.org/package/checkers})
      \item copied here from Section~\ref{sec:reuseable-pecs}:

@@

\begin{quote}
    \begin{itemize}
        \item Add "best current practice"
        \item We showed how to reuse pieces of specifications
    \end{itemize}
\end{quote}
